\documentclass[10pt,]{article}

\usepackage{changepage} % to indent block text
\usepackage[margin=0.75in]{geometry}
%\usepackage[left=0.75in, right=0.75in, top=1in]{geometry}



\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi




% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}


% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Matthew D. McHugh, PHD, JD, MPH, RN, FAAN - CV }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

\usepackage[none]{hyphenat}

% hanging paras
\usepackage{hanging}

% use bibtex for references
\usepackage[backend=bibtex,style=numeric]{biblatex}
\bibliography{mybib.bib}



% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Matthew D. McHugh, PHD, JD, MPH, RN, FAAN:  CV (Curriculum Vitae)},
            pdfauthor={Matthew D. McHugh, PHD, JD, MPH, RN, FAAN},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}
\raggedright

\centerline{\LARGE \sc Matthew D. McHugh, {\large PhD, JD, MPH, RN, FAAN}}

\vspace{2 mm}

\centerline{\large \sc Professor and Independence Endowed Chair for Nursing Education}

\vspace{2 mm}

\hrule
%\section{\Large \sc Contact Information}
\begin{tabular}{@{}p{3.5in}p{4in}}
University of Pennsylvania School of Nursing  & \hspace{1in} {\textit {Phone:}}  215-746-0205 \\  
Center for Health Outcomes and Policy Research & \hspace{1in} {\textit {email:}}  {\ttfamily \href{mailto:mchughm@nursing.upenn.edu}{\nolinkurl{mchughm@nursing.upenn.edu}}} \\              
Claire M. Fagin Hall · Rm 379  & \hspace{1in} {\textit {web:}} \href{https://www.nursing.upenn.edu/chopr}{\ttfamily www.nursing.upenn.edu/chopr}\\       
418 Curie Boulevard · Philadelphia, PA 19104-4217  & \hspace{1in} {\textit {Twitter:}} {\ttfamily @matthewdmchugh}\\     
\end{tabular}

\vspace{2 mm}

\hrule

\section{\Large \sc {Education}}
{\textit {Northeastern University School of Law} \hfill 2006 \newline
\hspace*{0.5cm} {\textbf {JD}} · Law

{\textit {University of Pennsylvania} \hfill 2004 \newline
\hspace*{0.5cm} {\textbf {PhD}} · Nursing 

{\textit {Harvard University}  \hfill	2003 \newline
\hspace*{0.5cm} {\textbf {MPH}} · Public Health (Health Policy and Management)
	
{\textit {University of Pennsylvania} \hfill 1998 \newline
\hspace*{0.5cm} {\textbf {MSN}} · Family Nurse Practitioner/Psych. Clinical Nurse Specialist

{\textit {Gwynedd-Mercy University} \hfill	1996 \newline
\hspace*{0.5cm} {\textbf {BSN}} · Nursing \newline

\section{\Large \sc{Post-Graduate Training \& Fellowships}}

Post-Doctoral Fellowship \hfill 2006-2008 \newline
Center for Health Outcomes and Policy Research · University of Pennsylvania  \newline
\hspace*{0.5cm} {\textit {Advanced Training in Nursing Outcomes Research} (T32-NR07104, L. Aiken, PI)
 
Graduate Research Fellow \hfill 2003-2005 \newline
Institute on Urban Health Research · Northeastern University  \newline
\hspace*{0.5cm} {\textit {Institute on Urban Health Research Fellowship} (H. Amaro, PI)

Fulbright Scholar \hfill 2001-2002 \newline
World Health Organization (WHO) · Regional Office for Europe, Copenhagen, Denmark  \newline
\hspace*{0.5cm} {\textit {The WHO Family Health Nurse Pilot Study}

Post-Masters Certification \hfill 1999 \newline
University of Pennsylvania School of Nursing · Philadelphia, PA  \newline
\hspace*{0.5cm} {\textit {Psychiatric-Mental Health Clinical Nurse Specialist} \newline

\section{\Large \sc{Academic Appointments}}

Professor of Nursing \hfill {2017-{\small{\sc{Present}}}} \newline
\hspace*{0.5cm} {\textit {University of Pennsylvania} · Philadelphia, PA

Associate Professor of Nursing \hfill 2013-2017 \newline
\hspace*{0.5cm} {\textit {University of Pennsylvania} · Philadelphia, PA

Assistant Professor of Nursing \hfill 2008-2012 \newline
\hspace*{0.5cm} {\textit {University of Pennsylvania} · Philadelphia, PA \newline

\section{\Large \sc{Administrative Positions}}

Associate Director  \hfill {2013-{\small{\sc{Present}}}} \newline
\hspace*{0.5cm} Center for Health Outcomes and Policy Research \newline
\hspace*{0.5cm} University of Pennsylvania

Faculty Director  \hfill {2010-{\small{\sc{Present}}}} \newline
\hspace*{0.5cm} {\textit {Dual Degree Program in Nursing and Health Care Management} \newline
\hspace*{0.5cm} University of Pennsylvania (Penn Nursing \& The Wharton School)

Faculty Director  \hfill {2010-{\small{\sc{Present}}}} \newline
\hspace*{0.5cm} {\textit {Nursing and Health Services Management minor} \newline
\hspace*{0.5cm} University of Pennsylvania (Penn Nursing \& The Wharton School) \newline

\section{\Large \sc{Other Appointments}}

Adjunct Faculty \hfill {2016-{\small{\sc{Present}}}} \newline
\hspace*{0.5cm} {\textit {Queensland University of Technology} · Queensland, Australia

Senior Fellow  \hfill {2008-{\small{\sc{Present}}}} \newline
\hspace*{0.5cm} {\textit {Leonard Davis Institute of Health Economics} · University of Pennsylvania

Senior Fellow  \hfill {2008-{\small{\sc{Present}}}} \newline
\hspace*{0.5cm} {\textit {Center for Public Health Initiatives} · University of Pennsylvania

Faculty Fellow  \hfill {2012-{\small{\sc{Present}}}} \newline
\hspace*{0.5cm} {\textit {Penn Institute on Urban Research} · University of Pennsylvania \newline

\section{\Large \sc{Honors, Awards, And Memberships In Honorary Societies}}

Independence Foundation Chair in Nursing Education \hfill {2017-{\small{\sc{Present}}}} \newline
\hspace*{0.5cm} {\textit {University of Pennsylvania}

Th 2017 IRGNI Research Mentor Award  \hfill 2017	\newline
\hspace*{0.5cm} {\textit {AcademyHealth Interdisciplinary Research Group on Nursing Issues (IRGNI)} 

2017 Commencement Speaker \hfill 2017	\newline
\hspace*{0.5cm} {\textit {Queensland University of Technology} · Queensland, Australia

President's Distinguished Alumni Award \hfill 2014 \newline
\hspace*{0.5cm} {\textit {Gwynedd-Mercy University}

2013	Top 10 Most Read Papers in {\textit {Health Affairs} \hfill 2013
\vspace{-2.5mm}
\begin{adjustwidth}{1cm}{1cm}
{\footnotesize {\textbf {McHugh, M. D., et al. (2013). Hospitals with higher nurse staffing had lower odds of readmissions penalties than hospitals with lower staffing. {\textit {Health Affairs, 32}}(10), 1740-1747.}}}
\end{adjustwidth}

The Rosemarie Greco Term Endowed Associate Professorship in Advocacy \hfill 2013-2017 \newline
\hspace*{0.5cm} {\textit {University of Pennsylvania}

Fellow of the American Academy of Nursing \hfill {2012-{\small{\sc{Present}}}}

Dean’s Award for Undergraduate Scholarly Mentorship \hfill 2012	

2011 Robert Wood Johnson Foundation’s Top 5 Most Influential Research Articles \hfill 2011 
\vspace{-2.5mm}
\begin{adjustwidth}{1cm}{1cm}
{\footnotesize {\textbf {McHugh, M. D., et al. (2011). Nurses’ widespread job dissatisfaction, burnout and frustration with health benefits signal problems for patient care. {\textit {Health Affairs, 30}}(2), 202-210.}}}
\end{adjustwidth}

Robert Wood Johnson Foundation Nurse Faculty Scholar \hfill 2011-2014	

The Family and Community Health Department Scholarship Award \hfill 2011 \newline
\hspace*{0.5cm} {\textit {University of Pennsylvania}

The Joan Lynaugh Faculty Mentorship Award \hfill 2010 \newline
\hspace*{0.5cm} {\textit {University of Pennsylvania}

\section{\Large \sc {Research}} 

\hspace*{0.25cm}{\textbf {\textit {Current Research Grants}}}

\textit {A Panel Study of Hospital Nursing Resources and Racial Disparities in Elder Outcomes} \hfill  9/2017--5/2020 \newline
{\hspace*{0.25cm}{\small{National Institute on Aging (2R01AG041099; {\textbf {McHugh, PI})}}} \hfill \$990,150 

\textit {The Impact of Nursing on Disparities in Surgical Patient Outcomes} ({\textbf{5{\small{th} {\small{\%-ile}}}}) \hfill 9/2017--8/2021 \newline
{\hspace*{0.25cm}{\small{National Institute of Minority Health \& Disparities (R01 XYZ); {\textbf {McHugh}}/Silber, MPIs)}}}	\hfill \$3,432,000

\vspace{4mm}

\hspace*{0.25cm}{\textbf {\textit {Pending Research Grants}}}

\textit {Advanced Training in Nursing Outcomes Research} ({\textbf{2{\small{nd} {\small{\%-ile}}}}) \hfill  7/2019--6/2024 \newline
{\hspace*{0.25cm}{\small{National Institute on Nursing Research (T32NR007104--21; Aiken, PI/{\textbf {McHugh, Co-I})}}} \hfill \$2,519,530

\vspace{4mm}

\hspace*{0.25cm}{\textbf {\textit {Past Funded Research Grants}}}

\textit {Graduate Nurse Education Demonstration} \hfill 8/2012--7/2018 \newline
{\hspace*{0.25cm}{\small{Centers for Medicare and Medicaid Services ({\textbf {McHugh}}/Aiken, MPIs)}}}	\hfill \$37.5 million

\vspace{4mm}

\hspace*{0.25cm}{\textbf {\textit {Doctoral Dissertation}}}

{\textit {The role of readiness for change in the residential treatment recovery outcomes among female adolescents with anorexia nervosa.}} 
2003-University of Pennsylvania; Chair-Margaret Cotroneo, PhD, APRN) (Dissertation Abstracts International No. AAT 3125871). {\textbf {\small {McHugh, M.D. (2007). Readiness for change and short-term outcomes of female adolescents in residential treatment for anorexia nervosa. {\textit {International Journal of Eating Disorders, 40}}(7), 602-612.}}}

\vspace{4mm}

\hspace*{0.25cm}{\textbf {\textit {Research Consultations}}}

{\textit {Impact of nursing on patient outcomes in Department of Defense hospitals}} \hfill 2016-18 \newline
\hspace*{0.5cm}U.S. Department of Defense, (Patrician, PI; {\textbf {McHugh}}, Consultant)

{\textit {Improving the Trauma System Response to Disaster}} \hfill 2006-2008 \newline
\hspace*{0.5cm}National Library of Medicine (R21-LM008700), (Branas, PI; {\textbf {McHugh}}, Consultant)

\vspace{4mm}

\section{\Large \sc{Publications}}
\hspace*{0.5cm}{\textbf {\small{Research, peer-reviewed (*data-based, {\underline{supervised student/fellow})}}}

%*author, A. A., {\underline {Student, A.}}, \& {\textbf {McHugh, M. D.} (year). Title. {\textit {Journal, Volume}}(Issue): pg-pgx.

%Use hanging paragraphs for publications

\begin{hangparas}{.25in}{1}

*Aiken, L. H., Sloane, D. M., {\underline {Barnes, H.}}, Cimiotti, J., Jarrin, O., \& {\textbf {McHugh, M. D.}} (2018). Nurses’ and patients’ appraisals show patient safety in hospitals is still deficient and recommended measures not implemented. {\textit {Health Affairs, 37}}(11): 1744-1751.

\end{hangparas}

\vspace{4mm}

\hspace*{0.5cm}{\textbf {\small{Monographs, Manuals, or Reports}}}

\begin{hangparas}{.25in}{1}

{\textbf {McHugh, M. D.}} (prepared for the Commonwealth of Pennsylvania Joint State Government Commission). (2015). {
\textit {Professional Bedside Nursing in Pennsylvania: A Staff Study.}} Joint State Government Commission.

\end{hangparas}

\vspace{4mm}

\hspace*{0.5cm}{\textbf {\small{Book chapters}}}

\begin{hangparas}{.25in}{1}

Clarke, S.P. \& McHugh, M.D. (2009). Measuring and managing outcomes. In D. L. Huber (Ed.), {\textit {Leadership and Nursing Care Management (4th ed.)}} Philadelphia: W.B. Saunders.

\end{hangparas}

\vspace{4mm}

\hspace*{0.5cm}{\textbf {\small{Abstracts, data-based and peer reviewed}}}

\begin{hangparas}{.25in}{1}

{\underline {White, E.}}, Aiken, L. H., \& {\textbf{McHugh, M. D.}} (2018, November). {\textit{The Impact of Registered Nurse Work Environment on Care Quality in Nursing Homes.}} Poster presentation at the Gerontological Society of America's 70th Annual Scientific Meeting, Boston, Massachusetts.

\end{hangparas}

\vspace{4mm}

\section{\Large \sc Recent Lectures, Speeches, And Workshops By Invitation}


{\textit {Nurse staffing a key to patient safety: Evidence from Queensland and around the world.}} \hfill 2018 
\vspace{-2.5mm}
\begin{adjustwidth}{0.5cm}{1cm}
Queensland University of Technology (QUT) School of Nursing 40th Anniversary Public Lecture. QUT, Brisbane, Queensland, Australia
\end{adjustwidth}

{\textit {Improving the Work Environment to Improve Clinician Well-Being and Reduce Burnout.}} \hfill 2018 
\vspace{-2.5mm}
\begin{adjustwidth}{0.5cm}{1cm}
National Academy of Medicine committee meeting on Systems Approaches to Improve Patient Care by Supporting Clinician Well-Being. National Academy of Medicine, Washington, DC
\end{adjustwidth}

{\textit {Solutions for an Ailing Health System.}} \hfill 2018 
\vspace{-2.5mm}
\begin{adjustwidth}{0.5cm}{1cm}
University of Pennsylvania “On the Road” Series. Penn Alumni - Southern California Regional Advisory Board, Los Angeles, CA
\end{adjustwidth}

\section{\Large \sc Professional Leadership and Memberships in Scientific Societies}

NIMHD Loan Repayment Grant Review Panel \hfill {2018-{\small{\sc{Present}}}}
\vspace{-2.5mm}
\begin{adjustwidth}{0.5cm}{1cm}
National Institute on Minority Health and Health Disparities (NIMHD) 
\end{adjustwidth}

AcademyHealth Outstanding Dissertation Award selection committee \hfill {2018-{\small{\sc{Present}}}}

NAM Action Collaborative on Clinician Well-Being and Resilience \hfill 2017
\vspace{-2.5mm}
\begin{adjustwidth}{0.5cm}{1cm}
Invited author for National Academy of Medicine Action Collaborative on Clinician Well-Being and Resilience conceptual model discussion paper
\end{adjustwidth}

\section{\Large \sc Service Activities at the University of Pennsylvania}
\vspace{-1mm}
\hspace*{0.5cm}{\textbf {\textit{\small{School of Nursing Committees}}}}\\
PhD Statistics Curriculum and Competencies taskforce, Chair \hfill {2018-{\small{\sc{Present}}}}\\
PhD Curriculum Committee, Member \hfill {2018-{\small{\sc{Present}}}}\\
Faculty Search Committee, Chair \hfill 2016- 2018\\

\vspace{2mm}
\hspace*{0.5cm}{\textbf {\textit{\small{University Committees}}}}\\ 
Center for Undergraduate Research and Fellowship’s Fulbright Program Advisor \hfill 2017\\	
Penn Population Aging Research Center Advisory Board \hfill {2015-{\small{\sc{Present}}}}\\

\section{\Large \sc Teaching}

\hspace*{0.5cm}{\textbf {\textit{\small{Course Director}}}} \\
{\textit{Current Issues in Health \& Social Policy} {\small{(Undergraduate/Graduate)}} \hfill 2017\\	
{\textit{Advances in Health Systems Research \& Analysis}} {\small{(Undergraduate)}} \hfill 2017\\

\vspace{2mm}
\hspace*{0.5cm}{\textbf {\textit{\small{Guest Lectures at Penn}}}}\\
{\textit{Secondary data analysis}}; Quantitative Research Designs and Method {\small{(PhD)}} \hfill 2018\\
{\textit{Nursing outcomes research}}; Pathways to Practice {\small{(Undergraduate)}} \hfill 2017	\\
{\textit{Secondary data analysis}}; Quantitative Research Designs and Method {\small{(PhD)}} \hfill 2018\\
{\textit{Nursing and health services research}}; Introduction to Statistics {\small{(Undergraduate)}} \hfill 2017\\

\vspace{2mm}
\hspace*{0.5cm}{\textbf {\textit{\small{Other Guest Lectures}}}}\\
{\textit{Introduction to public health policy}}; Introduction to Public Health---LaSalle University {\small{(Graduate)}} \hfill 2015\\

\section{\Large \sc Doctoral Dissertation Committees, Mentorship, \& Advising}}
\hspace*{0.5cm}{\textbf {\textit{\small{Early Career Faculty Mentorship}}}}\\
Dr. Hilary Barnes, Assistant Professor, University of Delaware \hfill Pending\\	
\hspace*{0.5cm}{\textit{The Impact of Nurse Practitioners on Health Outcomes in Outpatient Practices}}; AHRQ K08 mentor

Dr. Pam De Cordova, Assistant Professor, Rutgers University \hfill 2016--{\small{\sc{Present}}}\\
\hspace*{0.5cm}{\textit{Staffing SAFER - State Analysis for Effective Reporting}}; AHRQ K08-HS024339 mentor

Dr. Olga Jarrin, Assistant Professor; Rutgers University \hfill 2013-2015\\
\hspace*{0.5cm}{\textit{Comparative Effectiveness of Home Care Environments for Diverse Elders’ Outcomes}}; AHRQ K99-HS02240602 mentor


Post-Doctoral Fellows
2017- Present	Jordan Harrison, National Clinician Scholars Program (NCSP), University of Pennsylvania


2017- Present	Anna Krupp, National Clinician Scholars Program (NCSP), University of Pennsylvania

2017- Present	Heather Brom

2016- 2018	Jessica Smith
Current position: Assistant Professor; University of Texas at Arlington, College of Nursing and Health Innovation.





\pagebreak
\nocite{*}
\defbibheading{none}

\printbibliography[heading=none,keyword={presentation}]

some other text
\printbibliography[heading=none,keyword={paper}]

\end{document}